\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Yangqing(Gabrielle) Li}
\address{Unit 2526, 21 Wellesley College Rd, Wellesley, MA 02481}
\address{Citizenship: Chinese}
\address{(617) 459 - 3477 \\ yli16@wellesley.edu}

\begin{document}
\begin{center}
Updated July, 2021
\end{center} 


\begin{rSection}{Education}
{\bf WELLESLEY COLLEGE} \hfill {\em August, 2018 - Dec, 2021} 
\\ B.A in Mathematics, minor in Music (classical) \hfill { GPA: 3.95/4.00 (Major: 4.00/4.00) }
\\MATH 220 Probability
\\ MATH 225 Combinatorics and graph theory
\\ MATH 302 Elements in Analysis
\\ MATH 305 Abstract Algebra
\\ MATH 307 Topology
\\ MATH 310 Complex Analysis
\\ MATH 306 Galois Theory
\\ MATH 350 Functional Analysis (Independent study)
\\ MATH 350 Algebraic Topology II (Independent study)
\\
\\
{\bf MASSACHUSETTS INSTITUTE OF TECHNOLOGY} \hfill {\em August, 2019 - Dec, 2021} 
\\ Cross-registration\hfill { GPA: 5.00/5.00 }
\\ 6.006 Introduction to Algorithms
\\ 18.905 Algebraic Topology I (G)
\\ 18.715 Introduction to Representation Theory (G)
\\ 18.615 Introduction to Stochastic Process(G)
\\ 18.919 Graduate Topology Seminar - Kan Seminar (G, Fall 2021)\\ 
\end{rSection}




\begin{rSection}{Academic Experience}
{\bf Math REU participant}{, The University of Chicago} \hfill {\em June, 2021 - August, 2021}\\
I attended math lecture series on various topics.  My own work accumulated to a final talk on Steenrod algebra and an expository paper on Adams spectral sequence. Mentored by Professor J. Peter May and Dr Hana Jia Kong.

{\bf Women in Mathematics (WAM) participant}{, Institute for Advanced Study} \hfill {\em May, 2021}\\
I participated in seminars and lecture series on representation theory and categorification. 

{\bf Math REU participant}{, The University of Chicago} \hfill {\em June, 2020 - August, 2020}\\
I attended math lecture series on various topics.  My own work accumulated to a final talk on orientation theory of bundles and an expository paper on generalized bundle theory. Mentored by Professor J. Peter May and Hana Jia Kong.

{\bf Teaching assistant}{, Wellesley College Math Department} \hfill {\em January, 2019 - current}\\
I graded 200 and 300 level courses including combinatorics and graph theory, real analysis, topology, and complex analysis, provided feedback to the instructors, and held drop-in office hours. I am currently grading topology in fall 2021.

{\bf Student research assistant}{, Wellesley College Chemistry Department} \hfill {\em January, 2019 - July, 2019}\\
I performed simulations the impact of cosmic ice energetic processing on the synthesis of extraterrestrial prebiotic molecules in Christopher Arumainayagam’s computational chemistry lab.\\
\end{rSection}




\begin{rSection}{Expository talks}
{\bf Math REU Participant Talk}{, The University of Chicago}
\\Orientation theory of bundles \quad {\em (August, 2020)}
\\Adams spectral sequence \quad {\em (August, 2021)}

{\bf Kan Seminar}{, MIT}
\\ On Serre's \textit{Cohomologie modulo 2 des complexes d’Eilenberg-MacLane} \quad {\em (September, 2021)}
\\On Adams' \textit{Stable Homotopy Theory} \quad {\em (October, 2021)}
\\TBD \quad {\em (November, 2021)}\\
\end{rSection}




\begin{rSection}{Skills}
{\bf Programming languages and softwares}
\\C++ (proficient), \LaTeX (proficient), Python (intermediate), Java (intermediate)

{\bf Languages}
\\English(proficient), Chinese - Mandarin(native), Chinese - Cantonese(native), German(intermediate)\\ 
\end{rSection}




\begin{rSection}{Awards and Scholarships} 
{\bf Martha Davenport Heard Sophomore Prize in Mathematics}\\{Wellesley College Math Department
} \hfill{\em May, 2020}
\\Selected for excellence in mathematics coursework and contribution to the math department.

{\bf Introductory Chemistry Award}\\{Wellesley College Chemistry Department
} \hfill{\em February, 2019}
\\Selected for top performance in CHEM 120: Intensive introduction to chemistry.

\end{rSection}

\end{document}----------------------------

